\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-13 paper/draft.tex
Update section 2

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). % and unusually high code-reuse~\cite{npmstudy:19}. %, and a pressing need for usable dynamic analysis~\cite{}.
We develop a diverse set of analyses that target practical information about a program:
  an allow/deny security analysis,
  a profiling analysis showing bottlenecked modules,
  a synthesis-oriented analysis on input-output data, and
  an analysis enforcing a static union-based type system at runtime.
This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
We evaluate \sys at three different levels:
  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of four case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
\end{itemize}

@@

\subsection{Background on Modules and Module Systems}
\label{bg1}

languages provide module systems

closely coupled with the runtime

A module uses a \ttt{import} function and returns an export .
Intuitively a map

Several details:
  same module at multiple levels, and the module cache
  sometime it's the same, some times it;s not
  module resolution algorithm

@@

Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
  (i) an allow/deny security analysis,
  (ii) a profiling analysis showing hot modules,
  (iii) a synthesis-oriented analysis on input-output data, and
  (iv) an analysis enforcing a static union-based type system at runtime.
These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.

\heading{Security Analysis}
Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.

Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application. % and is exploitable.
Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
Other functionality is \emph{implicitly} provided by the programming language;
  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
Both explicitly and implicitly provided functionality is exploitable by third-party code.
While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
MLC shows great promise, as it can
(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).

To make this concrete, we are introducing

\heading{Performance Diagnosis}
Developers use various techniques to understand such problems.
For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
These techniques, however, require some degree of \emph{manual} effort:
  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.

Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
This allows viewing a series of calls as a stream of messages. % that 
% at each module boundary 
Module boundaries can be viewed as (virtual) queues of messages that await processing.
% and applying windowed average operations on a 
Overwhelming a module causes its ingress queue to grow.
% MM: related to the sync vs. async
% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.

To make this concrete, we are introducing

\heading{Type and Invariant Checking}
Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
Dynamic analysis can be used to generate type assertions or invariants
For example

To make this concrete, we are using
The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.

\heading{Learning, Synthesis, and Regeneration}
Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
Dynamic analysis can be used to generate type assertions or invariants
For example
The approach has been pioneered by systems such as

To make this concrete, we are using
The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.

@@

Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.

% , such as an object returned from a module or an exception about to be sent across the network.
Transformations can be applied to any value in the language. 
The most general value is an object, a bag of records holding key-value fields;
  other value types include primitives, functions, and booleans.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
More specifically,
  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.

The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
These skeletons provide hooks for end-developers writing analyses.
Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
These hooks are then extended or rewritten by developers to

For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
The wrappers depend on the intended goal:
  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.

\subsection{Disassembly}
\label{one}

@@

\subsection{Reassembly}
\label{three}

% \section{Applications of Analysis}
% \label{apps}

\section{Implementation: Lya}
\label{impl}

We implemented \sys for version 8.9.4 of the Node.js runtime.
Node.js is a runtime that bun

in about 1.5K lines of JavaScript.
We summarize where other implementations would diverge in table 1

Individual analysis are implemented using a set of templates that provide initial constructs (see below).
The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.

The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

In practice, the aforementioned dialysis stages can be implemented in two different ways.
The first is as a modified version of the runtime, where 
No-op analyses correspond to the default execution
  either 
It is introduced as a backward-compatible, drop-in replacement of the language's module system.
It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.

We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
  we expand on these at the end of this section~\sx{opportunities}.
% get second argument, no need to pass arguments around, tricky to 
% carefull hardcoding of paths, because \sys's code itself is split into modules
% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
% This is useful, for example, when...
% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;

(1) why node.js
(2) Create a table of compatibility and show individual aspects

\heading{Module System}
Node.js' module system is implemented entirely in JavaScript.
It exposes \ttt{require}, a global-looking function for importing modules.
\fixme{Figure} above demonstrates the use of \ttt{require}.

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% // -------------- [./main.js] -------------
% // importing point
% let Point = require("./point.js");
% Point.create(1, 1).print(); // => [1, 1]
% 
% // -------------- [./point.js] ------------
% let Point = function Point (x, y) {
%     this.x = x; this.y = y;
% };
% Point.prototype.print = function print () {
%   console.log([this.x, this.y]);
% };
% module.exports = {
%     create:  function create (x, y) {
%         return new Point(x, y);
%     }
% };
% \end{lstlisting}

In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
  the rest is module-private functionality.
Files and modules are in one-to-one correspondence (each file is treated as a separate module).
Method \ttt{require} is synchronous (\ie blocking):
  it will block execution until the module specified is loaded.
% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.

\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).

\subsection{Implementation of the Module System}
\label{c}

At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:

\begin{enumerate}
% \def\labelenumi{\arabic{enumi}.}
\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
\end{enumerate}

>>>>

\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\rf}[1]{\ref{#1}}
\newcommand{\se}[1]{\S\ref{#1}}
\newcommand{\fg}[1]{Fig.~\ref{#1}}

\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). % and unusually high code-reuse~\cite{npmstudy:19}. %, and a pressing need for usable dynamic analysis~\cite{}.
We develop a diverse set of analyses that target practical information about a program:
  an allow/deny security analysis,
  a profiling analysis showing bottlenecked modules,
% a synthesis-oriented analysis on input-output data,
  and an analysis extracting union-based type invariants.
This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
We evaluate \sys at three different levels:
  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
\end{itemize}

@@

\subsection{Background on Module Systems}
\label{bg1}

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
\caption{
  \textbf{Example of a library import.}
  \textmd{
    The program on the left imports the \ttt{simple-math} library, shown right, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
    Several names resolve to functionality provided by the programming language:
      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
  }
}
\label{fig:ex1}
\end{figure}

A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) provided by other developers sharing code others might find useful.
Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).

From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
% , as shown on line \fixme{XX},
% closely coupled with the runtime
% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.

From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
This process starts by locating the library in the file system % or across the network,\footnote{
%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
% }
by resolving relative or absolute identifiers.
% The library is assigned a unique identifier.
The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.

There is significant variation, but a few features are common across many implementations.
A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
The cache serves a dual purpose:
  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
These features complicate library-level analysis, especially in interpreted programming languages.

% Several details:
%   same module at multiple levels, and the module cache
%   sometime it's the same, some times it;s not
%   module resolution algorithm

@@

Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
  (i) an allow/deny security analysis,
  (ii) a performance-profiling analysis showing bottlenecked libraries, and
% (iii) a synthesis-oriented analysis on input-output data, and
  (iii) an analysis extracting runtime type invariants.
These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.

\heading{Security Analysis}
The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
Both bugs and malicious code in libraries create attack vectors, exploitable long after libraries reach their end-users.
As library boundaries disappear at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.

As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.

Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
Analyzing the behavior \emph{within} the library itself is not critical:
  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.

 %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
 %% % FIXME more about the policy, tracking arguments too
 %%  indicating the resources touched by that library 
 %% it seems critical to be able to toggle analysis on/off on production.
% \emph{
% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
% }

\heading{Performance Diagnosis}
Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{cheapcomplexity}.
Maintenance and rewriting can also cause performance regressions between two versions of a library;
% FIXME: Garbage collection
  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, performance characteristics can change dramatically~\cite{jest}.

As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain that can also affect other parts competing for the same resource~\cite{evp}.
Developers use various techniques to understand such problems---for example, they collect and replay traces against off-line versions of the system, or use statistical profiling to identify hot code-paths.
These techniques, however, require significant \emph{manual} effort:
  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.

Having the ability to quickly detect a slowdown and attribute it to a bottlenecked component is key, by toggling on/off a profiling analysis that operates at library boundaries.
The analysis would wrap library interfaces with logic that generates a model of the current workload.
Profiling can operate at a high resolution in time and space:
  (i) at every function call entering a library, and (ii) on hundreds of libraries across an application.
but does not need to track detailed operations such as direct variable accesses.
% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
Each library wrapper would collect profiling statistics at its own boundary, updating a global structure ordering the libraries' overall needs.

% \emph{
% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
% }

\heading{Type Invariant Discovery}
Extracting typing information is helpful in a variety of ways, as type safety is an important property helpful in variety of scenarios. 
%and types are lightweight annotations that can be quickly and efficiently checked.
For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (ii) guide program synthesis and regeneration~\cite{daikon}.
This is especially problematic in dynamic programming languages:
  in the absence of static type signatures, there is not much one can say about a object \ttt{o} without executing it and introspecting its properties.

As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
Given a value returned from a library call---say, a bignum or crypto library---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
if the type changes, because of a library version change or because of changes in the .

Dynamic analysis can be used to generate type assertions or invariants.
The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).

% would need to be able 
% to capture structural subtitling---that is the piecewise

% \heading{Learning, Synthesis, and Regeneration}

@@

% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}. The meta-function $\alpha$ stands for the locations of analysis hooks.
  }
}
\label{fig:base}
\end{figure}

% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
% The following subsections detail these steps.

\subsection{Dismantling}
\label{one}

When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc

It then dynamically replaces the implementation of\ttt{import}:
  rather than simply locating and loading a library, the function yields to \sys.

\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
% \omit{---the common case---}
Otherwise, \sys first invokes the built-in library loader to locate the library.

The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
A series of transformations is applied before and after interpretation~\sx{two}.

Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
\sys must note not to include these constructs in the ones 
% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
  the key to remember is that analysis are loaded from disk as source files, similar to libraries.

\begin{figure}[t]
\centering 
\includegraphics[width=0.45\textwidth]{./figs/lya_shadowing.pdf}
\caption{
  \textbf{Shadowing segments.}
  \textmd{
  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
  }
  \vspace{-4mm}
}
\label{fig:shadowing}
\end{figure}

@@

For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
This is achieved in three logical steps:
(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.

\heading{Transformations}
% , such as an object returned from a module or an exception about to be sent across the network.
Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
More specifically,
  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.

% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
% At runtime, $f'$ checks $\sigma$:
%  if the access is allowed, it forwards the call to $f$;
%  otherwise, it raises an exception.
% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
% 
% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
% 
% % Listing~\ref{core-tx} presents a simplified core of the language.
% 
% \begin{itemize}
% \item
%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
% \item
%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
% \item
%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
% \end{itemize}

Direct field accesses, such as assignments, require custom detection upon dereference.
To achieve this, \sys wraps fields with an interposition mechanism;
  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.

\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
  the unprocessed value is used to create objects, at runtime, that run a different analysis;
  the new value is used to revoke or chain analyses, a feature not explored further in this paper.

\heading{Context Transformation}
To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.

To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
Semantically, the context is a map from variable names to their values.
Thus, \sys creates an auxiliary hash table mapping names to transformed values.
Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.

%% FIXME: 
%% While user-defined global variables are stored in well-known locations,\footnote{
%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
%% } traversing the global scope for built-in values is generally not possible.
%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
%%   different lists exist for different environments and versions of the language.
%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.

Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).

\heading{Context Linking}
To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
The closure's body starts with a prologue of the form:
\begin{verbatim}
  local pint = ctx.print
  local error = ctx.error
  ...
\end{verbatim}
These statements shadow global variable names by redefining them as local ones.
The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
The prologue executes before everything else in the library.
% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.

Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
  these names are now bound to the correct library-local values.

\heading{Library Interface Transformation}
Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
The goal of the final transformation is to track activity at the boundary;
  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.

The final transformation is applied for every new consumer of the library.
This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.

\subsection{Re-assembly}
\label{three}

To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
The central mechanism for resolution is the library cache.
